\TITLE

### 2023-10-27 paper/main.tex
add pseudocodes and change sk and pk notation

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{float}
\usepackage{etoolbox}

\usepackage{url}
\usepackage{listings}
\usepackage{pdfpages}
\usepackage[english]{babel}
\usepackage{xcolor,colortbl}
\usepackage{scalerel}

@@

\begin{itemize}
\item There exists PKI infrastructure:
    \begin{itemize}
        \item The customer and the SP have their key pairs consisting of secret key $\mathrm{sk}(\mathrm{party})$ and public key $\mathrm{pk}(\mathrm{party})$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ for the customer and the SP accordingly.
        \item Both the customer and the SP can create and verify digital signatures created by the customer $\mathrm{sig}_{\mathrm{sk}(\mathrm{C})}$ and the SP $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$.
        \item The SP's public key $\mathrm{pk}(\mathrm{SP})$ is publicly known.
    \end{itemize}

@@

$$\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{provisionID}, \mathrm{pk(C)})$$

@@

\item $\mathrm{materials}$ - are the materials required to provide the service, for example, samples of urine, blood, stool, saliva; legal documents, CDs, emails, photos, bank statements; or any other type of material depending on the service.
\item $\mathrm{provisionID}$ - a randomly generated provision identifier, used to anonymously track the provision through all steps of the protocol.
\item $\mathrm{pk(C)}$ - the customer's public key used to encrypt the results published to the public storage network.
\end{itemize}

@@

\begin{eqnarray}
\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \\\\ \mathrm{address}, \mathrm{provisionID}, \mathrm{pk(C)}, \mathrm{sig}_\mathrm{SP} \; )\end{array}
\end{eqnarray}

@@

\item $\mathrm{T}_\mathrm{issue}$ - time at which the $\mathrm{PoD}$ is issued by the SP.
\item
  $\mathrm{T}_\mathrm{pay}$ - deadline for paying the transaction.
\item
  $\mathrm{T}_\mathrm{provide}$ - deadline to provide the result of the service, i.e. to publish $\mathrm{PoP}$.
\item $\mathrm{address}$ - payment address of the SP's anonymous blockchain account.
\item $\mathrm{provisionID}$ - the number that uniquely identifies the transaction previously generated by the customer.
\item $\mathrm{pk(C)}$ - the public key of the client used to encrypt the result published on the public storage network.
\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature to ensure non-repudiation.
\end{itemize}

@@

The customer collects all $\mathrm{materials}$ required by the SP, generates a random $\mathrm{provisionID}$ and a random keypair $(\mathrm{sk(C)},\mathrm{pk(C)})$. The $\mathrm{provisionID}$ is used to connect all actions associated with the transaction throughout the protocol. The $\mathrm{provisionID}$ and $\mathrm{pk(C)}$ are encoded as a QR code, printed and attached to the $\mathrm{pkg}$ package. The $\mathrm{sk(C)}$ is kept secret and is used to decrypt the $\mathrm{result}$ at the end of the protocol.

@@

The digital signature $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$ on the $\mathrm{PoD}$, created with the SP's secret key $\mathrm{sk}(\mathrm{SP})$, guarantees non-repudiation.

@@

@@

Symbolically: 
\[
\mathrm{PoD \gets get(provisionID)}
\]

@@

Symbolically: 
\[
\mathrm{receipt \gets payment(address)}
\]

@@

When the service is complete, a result should be generated. 
Next, the result is encrypted using a shared key derived from the customer's public key $\mathrm{pk(C)}$ and the SP's secret key $\mathrm{sk(S)}$ using the Diffie-Hellman key exchange (DHKE) method~\cite{diffieNewDirectionsCryptography1976}.
The encrypted result is then uploaded to the content addressable network (such as IPFS). In return, the content identifier ($\mathrm{cid}$) is created.

Symbolically: 
\[
\mathrm{cid \gets upload(E_{DHKE(sk(SP), pk(C))}(result))}
\]

@@

@@

Symbolically: 
\[
\mathrm{cid \gets get(provisionID)}
\]

@@

Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using a shared key derived from the customer's secret key $\mathrm{sk(C)}$ and the SP's public key $\mathrm{pk(S)}$ using the DHKE method. The protocol ends.

Symbolically: 
\[
\mathrm{result \gets D_{DHKE(sk(C), pk(SP))}(download(cid))}
\]

@@

\begin{itemize}
\item Neutral position (•): when a party has neither spent nor gained anything of significant value (money, time, effort). For example, at the beginning of the protocol.
\item Disadvantaged position (-): when a party has put a significant value without receiving an equivalent. For example, the customer has paid in advance for a service.
\item Advantaged position (+): when a party would benefit if the transaction was stopped at this step. For example, the SP has received payment before the service has been provided.
\end{itemize}

@@

\item Normal: taking actions prescribed by the protocol.
\item Abnormal: anything that deviates from the intended steps of the protocol. For example, sending an arbitrary message, skipping or repeating steps, or timing out.
\end{enumerate}

@@

\item Agree: the customer agrees with the action and therefore does not start a dispute.
\item Start a dispute: the customer disagrees with the action and therefore starts a dispute.
\end{enumerate}

@@

\begin{enumerate}
\item Both parties start from a neutral position ($\neutral$).
\item After completing a transaction, both parties end up in an advantageous position (\plus{}). In other words, they have an intrinsic motivation to initialise and complete the transaction.
\item The protocol steps are atomic - there are no intermediate steps.
\item The protocol can only go forward - there is no way to undo any action.
\item Repeating the first step starts a new transaction. Repeating any other step is considered abnormal and is ignored. For example, paying the invoice twice has no effect on the curse of the protocol.
\item Once published, the result is available to the customer on the storage network. 
\item Winning the dispute results in a neutral position ($\neutral$).
\item Losing the dispute results in a penalty greater than any reward, leading to a disadvantaged position (\minus{}). Therefore, the rational customer will not start a dispute that he is not sure he can win.
\item Both the customer and the SP are rational. They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral$ or \plus), but they are willing to risk a temporary worst position in favour of a later better position if and only if they can always get out of the worst position; in particular, the customer can always start a dispute and, if the SP has misbehaved, get out of the disadvantaged position (\minus) to the neutral position ($\neutral$).
\item We assume that the customer's materials without personal information are useless and the effort to deliver the package is negligible, so the customer's first step does not lead to a disadvantaged position.
\item We assume that the processing cost of publishing $\mathrm{PoD}$ is negligible and compensates for the customer's effort in delivering the package.
\end{enumerate}

@@

\begin{figure}[h!]
\includegraphics[width=\linewidth]{model.png}
\centering
\caption{Positions after each step of the protocol}
\label{fig:positions}
\end{figure}

The detailed description of each step and the rationale for the outcome of the result positions is given in Appendix~\ref{app:proof-of-fairness}.

@@

\begin{figure}[h!]
\includegraphics[width=\linewidth]{misbehaviour.png}
\centering
\caption{Transitions of positions where the SP is misbehaving and the customer starts a dispute}
\label{fig:misbehaviour}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=\linewidth]{rational.png}
\centering
\caption{Transitions of positions where both the customer and the SP follow the protocol}
\label{fig:rational}
\end{figure}

@@

Figure~\ref{fig:anonser-experiment1} and Figure~\ref{fig:anonser-experiment2} show the steps of the experiment. Their description is as follows:

@@

\ifx\FORMAT\SINGLECOLUMN
\noindent%
\begin{minipage}{\linewidth}
\makebox[\linewidth]{
\includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment1.pdf}}
\captionof{figure}{The steps of the experiment, the first part.}\label{fig:anonser-experiment1}
\end{minipage}

\noindent%
\begin{minipage}{\linewidth}
\makebox[\linewidth]{
\includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment2.pdf}}
\captionof{figure}{The steps of the experiment, the second part.}\label{fig:anonser-experiment2}
\end{minipage}
\else
\begin{figure*}
  \centering
  \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment1.pdf}
  \caption{The steps of the experiment, the first part.}\label{fig:anonser-experiment1}
\end{figure*}

\begin{figure*}
  \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment2.pdf}
  \caption{The steps of the experiment, the second part.}\label{fig:anonser-experiment2}
\end{figure*}

\fi
\subsection{Results}

>>>>

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{float}
\usepackage{etoolbox}
\usepackage{url}
\usepackage{listings}
\usepackage{pdfpages}
\usepackage[english]{babel}
\usepackage{xcolor,colortbl}
\usepackage{scalerel}

@@

\begin{itemize}
\item There exists PKI infrastructure:
    \begin{itemize}
        \item The customer and the SP have their key pairs consisting of secret key $\mathrm{sk}_\mathrm{party}$ and public key $\mathrm{pk}_\mathrm{party}$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ for the customer and the SP accordingly.
        \item Both the customer and the SP can create and verify digital signatures created by the customer $\mathrm{sig}_{\mathrm{sk}_\mathrm{C}}$ and the SP $\mathrm{sig}_{\mathrm{sk}_\mathrm{SP}}$.
        \item The SP's public key $\mathrm{pk}_\mathrm{SP}$ is publicly known.
    \end{itemize}

@@

$$\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{provisionID}, \mathrm{pk_C})$$

@@

\item $\mathrm{materials}$ - are the materials required to provide the service, for example, samples of urine, blood, stool, saliva; legal documents, CDs, emails, photos, bank statements; or any other type of material depending on the service.
\item $\mathrm{provisionID}$ - a randomly generated provision identifier, used to anonymously track the provision through all steps of the protocol.
\item $\mathrm{pk_C}$ - the customer's public key used to encrypt the results published to the public storage network.
\end{itemize}

@@

\begin{eqnarray}
\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{pk_C}, \mathrm{provisionID},  \mathrm{sig}_\mathrm{SP}, \mathrm{paymentAddress}, \\\\ 
\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}\; )\end{array}
\end{eqnarray}

@@

\begin{itemize}
\item $\mathrm{pk_C}$ - the public key of the client used to encrypt the result published on the public storage network.
\item $\mathrm{provisionID}$ - the number that uniquely identifies the transaction previously generated by the customer.
\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature to ensure non-repudiation.
\item $\mathrm{paymentAddress}$ - payment address of the SP's anonymous blockchain account.
\item $\mathrm{T}_\mathrm{issue}$ - time at which the $\mathrm{PoD}$ is issued by the SP.
\item
  $\mathrm{T}_\mathrm{pay}$ - deadline for paying the transaction.
\item
  $\mathrm{T}_\mathrm{provide}$ - deadline to provide the result of the service, i.e. to publish $\mathrm{PoP}$.
\end{itemize}

@@

The customer collects all $\mathrm{materials}$ required by the SP, generates a random $\mathrm{provisionID}$ and a random keypair $(\mathrm{sk_C},\mathrm{pk_C})$. The $\mathrm{provisionID}$ is used to connect all actions associated with the transaction throughout the protocol. The $\mathrm{provisionID}$ and $\mathrm{pk_C}$ are encoded as a QR code, printed and attached to the $\mathrm{pkg}$ package. The $\mathrm{sk_C}$ is kept secret and is used to decrypt the $\mathrm{result}$ at the end of the protocol.

@@

The digital signature $\mathrm{sig}_{\mathrm{sk}_\mathrm{SP}}$ on the $\mathrm{PoD}$, created with the SP's secret key $\mathrm{sk}_\mathrm{SP}$, guarantees non-repudiation.

@@

The Algorithm~\ref{alg:proofOfDelivery} presents the process of processing the PoD and recording it on-chain.

\begin{algorithm}
\caption{Algorithm for Registering Proof of Delivery}
\label{alg:proofOfDelivery}
\begin{algorithmic}[1]
\Function{proofOfDelivery}{$pk_C$, $provisionId$, $sig_{SP}$, $paidInCash$, $paymentAddress$, $paymentWindow$, $provisionWindow$}
    \State Verify $sig_{SP}$
    \If{provisions[$pk_C$][$provisionId$].exist}
        \State \Return Error("Provision already exists")
    \EndIf

    \If{$paidInCash = \text{TRUE} \oplus paymentAddress$ is not empty}
        \State \Return Error("Inconsistent payment method and address")
    \EndIf

    \State $\mathrm{T}_\mathrm{issue} \gets$ block.timestamp
    \State $\mathrm{T}_\mathrm{pay} \gets \mathrm{T}_\mathrm{issue} + paymentWindow$
    \State $\mathrm{T}_\mathrm{provide} \gets \mathrm{T}_\mathrm{issue} + provisionWindow$

    \State $provision \gets \left\{ \mathrm{T}_\mathrm{issue}, paymentDeadlineTime, \right.$
    \State \hspace{\algorithmicindent}$\left. \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, paidInCash, paymentAddress \right\}$
    \State provisions[$pk_C$][$provisionId$] $\gets provision$
\EndFunction
\end{algorithmic}
\end{algorithm}

@@

Symbolically: 
\[
\mathrm{PoD \gets get(pk_C, provisionID)}
\]

@@

Symbolically: 
\[
\mathrm{receipt \gets payment(paymentAddress)}
\]

@@

When the service is complete, a result should be generated. 
Next, the result is encrypted using a shared key derived from the customer's public key $\mathrm{pk_C}$ and the SP's secret key $\mathrm{sk(SP)}$ using the Diffie-Hellman key exchange (DHKE) method~\cite{diffieNewDirectionsCryptography1976}.
The encrypted result is then uploaded to the content addressable network (such as IPFS). In return, the content identifier ($\mathrm{cid}$) is created.

Symbolically: 
\[
\mathrm{cid \gets upload(E_{DHKE(sk_{SP}, pk_C)}(result))}
\]

@@

The Algorithm~\ref{alg:proofOfProvision} presents the process of processing the PoP and recording it on-chain.

\begin{algorithm}
\caption{Algorithm for Registering Proof of Provision}
\label{alg:proofOfProvision}
\begin{algorithmic}[1]
\Function{proofOfProvision}{$pk_C$, $provisionId$, $cid$}
    \State $provision \gets$ provisions[$pk_C$][$provisionId$]
    \If{not $provision$.exist}
        \State \Return Error("Provision must be created with proof of delivery first")
    \EndIf

    \State Update $provision$ with $\{cid\}$
\EndFunction
\end{algorithmic}
\end{algorithm}

@@

Symbolically: 
\[
\mathrm{cid \gets get(pk_C, provisionID)}
\]

@@

Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$ using a shared key derived from the customer's secret key $\mathrm{sk_C}$ and the SP's public key $\mathrm{pk_{SP}}$ using the DHKE method. The protocol ends.

Symbolically: 
\[
\mathrm{result \gets D_{DHKE(sk_C, pk_{SP})}(download(cid))}
\]

@@

\begin{itemize}
\item \textbf{Neutral position ($\neutral{}$)}: when a party has neither spent nor gained anything of significant value (money, time, effort). For example, at the beginning of the protocol.
\item \textbf{Disadvantaged position ($\minus{}$)}: when a party has put a significant value without receiving an equivalent. For example, the customer has paid in advance for a service.
\item \textbf{Advantaged position ($\plus{}$)}: when a party would benefit if the transaction was stopped at this step. For example, the SP has received payment before the service has been provided.
\end{itemize}

@@

\item \textbf{Normal}: taking actions prescribed by the protocol.
\item \textbf{Abnormal}: anything that deviates from the intended steps of the protocol. For example, sending an arbitrary message, skipping or repeating steps, or timing out.
\end{enumerate}

@@

\item \textbf{Agree}: the customer agrees with the action and therefore does not start a dispute.
\item \textbf{Start a dispute}: the customer disagrees with the action and therefore starts a dispute.
\end{enumerate}

@@

\begin{enumerate}
\item Both parties start from a neutral position ($\neutral${}).
\item After completing a transaction, both parties end up in an advantageous position (\plus{}). In other words, they have an intrinsic motivation to initialise and complete the transaction.
\item The protocol steps are atomic - there are no intermediate steps.
\item The protocol can only go forward - there is no way to undo any action.
\item Repeating the first step starts a new transaction. Repeating any other step is considered abnormal and is ignored. For example, paying the invoice twice has no effect on the curse of the protocol.
\item Once published, the result is available to the customer on the storage network. 
\item Winning the dispute results in a neutral position ($\neutral${}).
\item Losing the dispute results in a penalty greater than any reward, leading to a disadvantaged position (\minus{}). Therefore, the rational customer will not start a dispute that he is not sure he can win.
\item Both the customer and the SP are rational. They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral${} or \plus), but they are willing to risk a temporary worst position in favour of a later better position if and only if they can always get out of the worst position; in particular, the customer can always start a dispute and, if the SP has misbehaved, get out of the disadvantaged position (\minus) to the neutral position ($\neutral${}).
\item We assume that the customer's materials without personal information are useless and the effort to deliver the package is negligible, so the customer's first step does not lead to a disadvantaged position.
\item We assume that the processing cost of publishing $\mathrm{PoD}$ is negligible and compensates for the customer's effort in delivering the package.
\end{enumerate}

@@

\begin{figure}[h!]
\includegraphics[width=\linewidth]{model.png}
\centering
\caption{Visual representation of the fairness of the protocol. The figure shows the game-theoretic outcomes of each party after each possible actions taken. Symbol $\neutral${} represents neutral outcome, \minus{} represents disadvantaged outcome, and \plus{} represents advantaged outcome, where the order relation holds \minus{} < $\neutral${} < \plus{}.}
\label{fig:positions}
\end{figure}

The detailed description of each step and the rationale for the outcome is given in Appendix~\ref{app:proof-of-fairness}.

@@

\begin{figure}[h!]
\includegraphics[width=\linewidth]{misbehaviour.png}
\centering
\caption{Transitions of positions where the SP is misbehaving and the customer starts a dispute.}
\label{fig:misbehaviour}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=\linewidth]{rational.png}
\centering
\caption{Transitions of positions where both the customer and the SP follow the protocol.}
\label{fig:rational}
\end{figure}

@@

The experiment was conducted as follows:

@@

\subsection{Results}
